Ubercalibration Simulations \\(Euclid)

### 2011-01-27 Documentation/ubercal.tex
euclid: documentation update
git-svn-id: svn+ssh://astrometry.net/svn/trunk/projects/euclid@17300 03a3cea6-2c03-0410-ac9b-9271b1c66c29
euclid: documentation update
git-svn-id: svn+ssh://astrometry.net/svn/trunk/projects/euclid@17301 03a3cea6-2c03-0410-ac9b-9271b1c66c29
euclid: documentation
git-svn-id: svn+ssh://astrometry.net/svn/trunk/projects/euclid@17311 03a3cea6-2c03-0410-ac9b-9271b1c66c29

\documentclass[12pt,a4paper,twoside]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{color}
\usepackage{listings}

@@

\section{Sky Catalog}
The

@@

\subsection{Uncertainty Inverse-Variance}

\subsection{Catalog to Measured Flux Conversion}

@@

\subsection{Flat-Field Refinement: \textbf{\textit{p\_step}}}
The flat-field parameters can now be refined with the latest star flux estimates. Minimise error function with respect to the...

Consider all measurements

\begin{equation}
\chi^2 = \sum_{all~i} \frac{(c_i-f_{ij}s_{kj})^2}{{\sigma_i}^2}
\end{equation}

\begin{equation}
f_{ij} = \sum_{l = 1}^L q_{lj} g_i(\vec{x_i})
\end{equation}

\begin{equation}
\chi^2 = \sum_{all~i} \frac{(c_i- s_{kj} \sum_{l = 1}^L q_{lj} g_i(\vec{x_i}))^2}{{\sigma_i}^2}
\end{equation}

\begin{equation}
\frac{d\chi^2}{dq_{lj}} = \sum_{all~i} \frac{-2 g_l(\vec{x_i}) s_{kj+1} (c_i- s_{kj} \sum_{l = 1}^L q_{lj} g_i(\vec{x_i}))}{{\sigma_i}^2} = 0
\end{equation}

\begin{equation}
\sum_{all~i} \frac{g_l(\vec{x_i}) s_{kj+1} c_i}{{\sigma_i}^2} = \sum_{all~i} \frac{g_l(\vec{x_i}) s_{kj+1}^2 \sum_{l = 1}^L q_{lj+1} g_l(\vec{x_i})}{{\sigma_i}^2}
\end{equation}

>>>>

\documentclass[12pt,a4paper,twoside]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{color}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{upgreek}

@@

\section{Sky Catalog}
We create a fake sky, based on realistic star densities, between a magnitude of 19 to 22.5. The upper and lower limits are defined based the saturation and 10$\upsigma$ limits for a single Euclid exposure. Star's are generated with random coordinates (within the sky region being investigated) and with a random magnitude according to the following powerlaw:
\begin{equation}
\frac{1}{N} \frac{dN}{dm} = A + B m
\end{equation}

The \textit{Transformation Method} is used generate random numbers with the appropriate probability density function.

\begin{equation}
\log_{10} \frac{\Delta N}{\Delta m} = A + B m
\end{equation}

\begin{equation}
\frac{d N}{d m} =10^ {A + B m}
\end{equation}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=\textwidth]{source_mag_histogram.png}
\end{center}
\caption{A histogram of the generated star magnitudes. The number of stars is given by... XX \label{fig:source_magnitude}}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=\textwidth]{gods_sky.png}
\end{center}
\caption{A small subset of the simulated sky catalog produced. \label{fig:gods_sky}}
\end{figure}

The random number generate is given the same seed, so that the same simulated sky is produced each time the routine is called.

@@

\subsection{Uncertainty Inverse-Variance}
\begin{figure}[ht]
\begin{center}
\includegraphics[width=\textwidth]{flux_uncertainty_variance.png}
\end{center}
\caption{XX UPDATE \label{fig:flux_uncertainty}}
\end{figure}
\subsection{Catalog to Measured Flux Conversion}

@@

\subsection{Flat-Field Refinement: \textbf{\textit{p\_step}}}
The flat-field parameters can now be refined with the latest star flux estimates. To do this we minimize the error function for all measurements with respect to the flat-field parameters.

\begin{equation}
\chi^2 = \sum_{i} \frac{(c_i-f_{ij}s_{kj+1})^2}{{\sigma_i}^2}
\end{equation}

\begin{equation}
f_{ij} = \sum_{l = 1}^L q_{lj} g_l(\vec{x_i})
\end{equation}

\begin{equation}
\chi^2 = \sum_{i} \frac{(c_i- s_{kj+1} \sum_{l = 1}^L q_{lj} g_l(\vec{x_i}))^2}{{\sigma_i}^2}
\end{equation}

\begin{equation}
\frac{d\chi^2}{dq_{lj}} = \sum_{i} \frac{-2 g_l(\vec{x_i}) s_{kj+1} (c_i- s_{kj+1} \sum_{l' = 1}^{L'} q_{l'j} g_{l'}(\vec{x_i}))}{{\sigma_i}^2} = 0
\end{equation}

\begin{equation}
\sum_{i} \frac{g_l(\vec{x_i}) s_{kj+1} c_i}{{\sigma_i}^2} = \sum_{i} \frac{g_l(\vec{x_i}) s_{kj+1}^2 \sum_{l' = 1}^{L'} q_{l'j+1} g_{l'}(\vec{x_i})}{{\sigma_i}^2}
\end{equation}
